\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{setspace}
\usepackage{natbib}

\doublespacing

\title{Example Article Title: A Demonstration of APA 7 Format}
\author{Author Name}
\date{\today}

\doublespacing

\title{Example Article Title: A Demonstration of APA 7 Format}
\author{Author Name}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract of your article. The abstract should be a brief summary of the entire paper, including the purpose of the study, methods, results, and conclusions. The abstract should be no more than 250 words and should present the key findings concisely.

\noindent \textbf{Keywords:} keyword 1, keyword 2, keyword 3
\end{abstract}

\section{Introduction}

This is the introduction section. Here you should provide context for your research, explain the problem you are addressing, and state your research questions or hypotheses. The introduction should lead the reader from a general topic to your specific research focus.

\subsection{Literature Review}

Review the relevant literature in this subsection. You can cite sources like this \citep{smith2023example}.

\subsection{Research Questions}

State your research questions or hypotheses that guide your study.

\section{Methods}

Describe your research methodology in this section.

\subsection{Participants}

Describe your study participants here, including demographics and selection criteria.

\subsection{Procedures}

Explain the procedures you followed in conducting your research.

\subsection{Data Analysis}

Describe how you analyzed your data.

\section{Results}

Present your findings in this section. You can include tables and figures as needed.

\section{Discussion}

Discuss what your findings mean, how they relate to existing literature, and what implications they have for nursing practice or future research.

\subsection{Limitations}

Acknowledge the limitations of your study.

\subsection{Implications}

Discuss the implications of your findings for nursing practice, education, or research.

\section{Conclusion}

Summarize your key findings and their significance in this conclusion section.

\bibliography{references}
\bibliographystyle{plainnat}

\end{document}

